Is the direction of Granger causal influence the same as the direction of information flow?

### 2015-07-07 paper.tex
Make minor fixes.

Granger causality, as originally described by Granger~\cite{Granger1969InvestigatingCausal}, measures the level of influence that one process $\{X\}$ has on another process $\{Y\}$. The analysis compares the \emph{error in predicting} the $\{Y\}$ process based on (i) simply the past of $\{Y\}$, and (ii) based on the past of both $\{X\}$ and $\{Y\}$. The Granger causality metric is the ratio of these errors, encapsulating the innovations that the process $\{X\}$ causally supplies to the process $\{Y\}$. Many variations of Granger causality have also been considered, including a generalization -- Directed Information (see~\cite{MasseyCausality,quinn,weissman}) -- an information-theoretic quantity denoted by $I(\m{X}\to\m{Y})$. These form possible alternatives for estimating the direction of causal influence, but Directed Information is a generalization of many of these metrics~\cite{quinn}.

@@

In the presence of noise in the feedback link, restricting our attention to linear strategies, we can use a simple modification of the Schalkwijk-Kailath strategy, incorporating the feedback\footnote{We note that implicitly, this strategy assumes an energy/SNR constraint on the feedback link. This is because the receiver simply sends back the estimate, which is shown to converge to the true value of $\Theta$.}. The receiver still simply transmits the estimate $\widehat{\Theta}_i$ based on the $i$-th forward channel output $Y_i=X_i+N_i$. The transmitter now receives corrupted versions $Z_i=\widehat\Theta_{i-1} + R_{i-1}$ of the receiver's transmissions. That is,
\begin{align}
	& \text{Transmitter's transmissions:}\;X_i = \Theta - (\widehat\Theta_{i-1} + R_{i-1}) \\ \label{eq:noisy-tx-x}
	& \text{Channel outputs at the receiver:}\;	Y_i = X_i + N_i \\
	& \text{Receiver's estimates \& transmissions:}\;	\widehat\Theta_i = \widehat\Theta_{i-1} + \frac{Y_i}{i}
\end{align}
where $R_{i-1}$ is the AWGN noise in the reverse link. $R_i \sim \mathcal{N}(0, \sigma_R^2)$ are iid random variables.

>>>>

Granger causality, as originally described by Granger~\cite{Granger1969InvestigatingCausal}, measures the level of influence that one process $\{X\}$ has on another process $\{Y\}$. The analysis compares the \emph{error in predicting} the $\{Y\}$ process based on (i) simply the past of $\{Y\}$, and (ii) based on the past of both $\{X\}$ and $\{Y\}$. The Granger causality metric is the ratio of these errors, encapsulating the innovations that the process $\{X\}$ causally supplies to the process $\{Y\}$. Many variants of Granger causality have also been considered, including a generalization -- Directed Information (see~\cite{MasseyCausality,quinn,weissman}) -- an information-theoretic quantity denoted by $I(\m{X}\to\m{Y})$. These variants form possible alternatives for estimating the direction of causal influence, but Directed Information is a generalization of many of these metrics~\cite{quinn}.

@@

In the presence of noise in the feedback link, restricting our attention to linear strategies, we can use a simple modification of the Schalkwijk-Kailath strategy, incorporating the feedback\footnote{We note that implicitly, this strategy assumes an energy/SNR constraint on the feedback link. This is because the receiver simply sends back the estimate, which is shown to converge to the true value of $\Theta$.}. The receiver still simply transmits the estimate $\widehat{\Theta}_i$ based on the $i$-th forward channel output $Y_i=X_i+N_i$. The transmitter now receives corrupted versions $Z_i=\widehat\Theta_{i-1} + R_{i-1}$ of the receiver's transmissions. That is,
\begin{align}
	& \text{Transmitter's transmissions:}\;X_i = \Theta - (\widehat\Theta_{i-1} + R_{i-1}) \\ \label{eq:noisy-tx-x}
	& \text{Channel outputs at the receiver:}\;	Y_i = X_i + N_i \\
	& \text{Receiver's estimates \& transmissions:}\;	\widehat\Theta_i = \widehat\Theta_{i-1} + \frac{Y_i}{i}
\end{align}
where $R_{i-1}$ is the AWGN noise in the reverse link. $R_i \sim \mathcal{N}(0, \sigma_R^2)$ are iid.\ random variables.
